Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-16 2017-Xudong-SMT/FM-2018-extended.tex
OA fig

%{s0---delta-->s0},   {---:hb_P:12:1-->},   (:ra:11:1=l)/\(delta=:ra:11:1)/\(var_s0=0)/\(:hb_P:12:1=a1:sva_SV0:1:1)/\(:ra:1:1=a1:sva_SV0:1:1)/\(a1:sva_SV0:1:1!=delta(x)),   {var_s0 := 1}
$\begin{array}{r@{}l}
    ot  = &\openrule{\{0 \xrightarrow{\OTvar{resume(false)}} 0, 0 \xrightarrow{\OTvar{start(true)}} 1\}, ~~\{\xrightarrow{hb}\},~~\OTvar{resume(false)}=\OTvar{failure(}\OTvar{b}_1\OTvar{)}\\
    			     \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)} \OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)} \OTland \OTvar{v}=\OTvar{\underline{fail}}\\
			     \OTland \OTvar{b}_1 = \OTvar{b}_2 \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
    	   {\ostate{00} \xrightarrow{\OTvar{v}} \ostate{01}}\\
  \end{array}$
\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
\end{figure}

@@

The resulting open transitions represent all the
possible movements of the LOTOS example.
What can be observed is any actions of the process $P$ from the beginning, until $P$ performs a $\delta(x)$ and the value of
$x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ then $ot_2$. 
Then it keeps presenting the behavior of $Q$, as seen in $ot_3$. 
%The $ot_1$ transition means that the actions of the process $P$ could
%be transmitted out, until $P$ performs a $\delta(x)$ and the value of
%$x$ is transmitted, through transition
%$ot_2$. The other 3 open transitions shows the behaviors of the
%process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the
%controller has already set the value $s_0$ to 1 in the previous
%action.

\begin{figure}[t]
   \centerline{\includegraphics[width=12cm]{XFIG/BIPresult-ArchFailureTimerMax}}
   \caption{Open Automaton\TODO{syntax could be better...}}  \label{schema:resultOA}
 \end{figure}

@@

\TODO{Change perspective: we are working on the formal extensino of
  BIB architectures, and their semantics in terms of pNets. Then
  bisimulation and model-checking principles adapted to open pNet
  systems are under development}

@@

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, frame=single]
   {s0---failure(true)-->s1, t0---start(true)-->t1}, {---:hb_B:13:1-->},
   (failure(true)=failure(b1:sva_SV0:1:1))/\(start(true)=start(b2:sva_SV0:1:1))
   /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
   /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1),
   {t := 4}
OT ------------------------------------------------------------
        <s0_t0>-----:ra:1:1----><s1_t1>

@@

   {s1---failure(false)-->s1, t1---start(false)-->t1},   {---:hb_B:13:1-->},
   (failure(false)=failure(b1:sva_SV0:1:1))/\(start(false)=start(b2:sva_SV0:1:1))
   /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
   /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1), {}
OT ------------------------------------------------------------
        <s1_t1>-----:ra:1:1----><s1_t1>

>>>>

%{s0---delta-->s0},   {---:hb_P:12:1-->},   (:ra:11:1=l)/\(delta=:ra:11:1)/\(var_s0=0)/\(:hb_P:12:1=a1:sva_SV0:1:1)/\(:ra:1:1=a1:sva_SV0:1:1)/\(a1:sva_SV0:1:1!=delta(x)),   {var_s0 := 1}
$\begin{array}{r@{}l}
    ot  = &\openrule{\{0 \xrightarrow{\OTvar{resume(false)}} 0, 0 \xrightarrow{\OTvar{start(true)}} 1\}, ~~\{\xrightarrow{hb}\},~~\OTvar{resume(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
    			     \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)} \OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)} \OTland \OTvar{v}=\OTvar{\underline{fail}}\\
			     \OTland \OTvar{b}_1 = \OTvar{b}_2 \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
    	   {\ostate{00} \xrightarrow{\OTvar{v}} \ostate{01}}\\
  \end{array}$
\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
\end{figure}

@@

To improve the readability of this figure, we used the following conventions:
we omit the transitions of the two pLTS, and the set of ``working''
holes; and we directly write the resulting action as first element of
each OT, rather than including it as an equality inside the
predicate. 
\TODO{missing some comments on this result OA}.

\begin{figure}[t]
   \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerOA}}
   \caption{Open Automaton}  \label{schema:resultOA}
 \end{figure}

@@

\TODO{Change perspective: we are working on the formal extension of
  BIB architectures, and their semantics in terms of pNets. Then
  bisimulation and model-checking principles adapted to open pNet
  systems are under development}

@@

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, frame=single]
   {s0---fail(true)-->s1, t0---start(true)-->t1}, {---:hb_B:13:1-->},
   (fail(true)=fail(b1:sva_SV0:1:1))/\(start(true)=start(b2:sva_SV0:1:1))
   /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
   /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1),
   {t := 4}
OT ------------------------------------------------------------
        <s0_t0>-----:ra:1:1----><s1_t1>

@@

   {s1---fail(false)-->s1, t1---start(false)-->t1},   {---:hb_B:13:1-->},
   (fail(false)=fail(b1:sva_SV0:1:1))/\(start(false)=start(b2:sva_SV0:1:1))
   /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
   /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1), {}
OT ------------------------------------------------------------
        <s1_t1>-----:ra:1:1----><s1_t1>
